Variable Selection

### 2015-06-19 var_select.rmd
var_select finished numeric vars

```{r, echo=FALSE, include=FALSE}
setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
library('ggplot2', lib = 'C:/Progra~1/R/R-3.1.2/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
library('magrittr',lib='C:/Progra~1/R/R-3.1.3/library')
library('reshape2',lib='C:/Progra~1/R/R-3.1.3/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.0/library')
library('car')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.0/library')
```

@@

```{r, echo=FALSE}
# try deleting very high return.pdol values greater than 3
test<- all7 %>% filter(return.pdol <=3 & return.pdol> -2)
qqPlot(test$return.pdol)
qqPlot(log(test$return.pdol+.97))
#have a look at the shape of return.pdol as bar graph
ggplot(test, aes(x=return.pdol)) + geom_histogram(aes(y=..density..), binwidth=.1)
ggplot(test, aes(x=log(test$return.pdol+.97))) + geom_histogram(aes(y=..density..), binwidth=.1)
```

@@

```{r}
### delete outliers! and variables that aren't by milestone
all7a<- all7 %>% filter(return.pdol <=3 & return.pdol> -2)
all7a<- all7 %>% select(-Paperless,-Innovation, -JobInvCount,-job.first.inv.email.Sent, 
                        -Total.Costs..AUD., -Stage, -Folders, -Total.Fee, -Disburse, -Subcon.fee,
                        -Job.Size, -Tot.Invoiced, -charge, -cost, -Dis.subcon, -hours,-profit,-balance,
                        -Role)

@@

```{r, echo=TRUE}
BT.lin<- function(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') {
        formula = paste("return.pdol ~ inv.mlsto + Discipline + client.count + Business +
                              Biz.size + Biz.type + Year + Num.days +
                              no.users + pc.contracttech + client.neginv + client.numinv + client.totinv +
                              pc.director + pc.midtech + pc.midpro + pc.gradpro + pc.seniortech + pc.seniorpro +
                              pc.pro + mean.peeps + hours.perday + num.inv + mean.inv + num.neginv + client.meaninv +
                              code.director + ProjEng.Pos", add.var, sep="+")
        if (type== 'aov') {
            model= aov(as.formula(formula)              
                      ,data= data)
            return(summary(model)) 
        }
        else{
                model=lm(as.formula(formula)                     
                        ,data= data)
                df<- as.data.frame(summary(model)$coefficients)
                df$var<-rownames(summary(model)$coefficients)
                colnames(df)[names(df) %in% 'Pr(>|t|)']<-'Pval'
                return(df %>% arrange(-abs(Estimate)))

@@

BT.lin(type= 'lm', data= all7a[1:1313,], add.var = 'Job.Type.Primary') %>% slice(1:20)
BT.lin(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') %>% slice(1:10)
BT.lin(type= 'lm', data= all7a[1314:2283,], add.var = 'Job.Type.Primary') %>% slice(1:10)
BT.lin(type= 'aov', data= all7a, add.var = 'Job.Type.Primary')
BT.lin(type= 'aov', data= all7a[1314:2283,], add.var = 'Job.Type.Primary')

@@

Most influential variables are:
* Business type
* director code
* Discipline
* Biz.type

Excluded variables include:
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Primary
* Job.Detail.Secondary
* Job.Type.Primary
* Job.Type.Secondary
* State
* Type
* no.employees
* contact.count
* JD.Primary
* JD.Second
* dist
* timespan (won't know to begin with)
* Num.disc
* Inv.freq
* client.invfreq

>>>>

```{r, echo=FALSE, include=FALSE}
library('knitr')
# library('knitr', lib = 'C:/Progra~1/R/R-3.1.2/library')
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.1.2/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.1.3/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.1.3/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.0/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.0/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.0/library')

library('ggplot2')
library("dplyr")
library("plyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
```

@@

```{r}
# try deleting very high return.pdol values greater than 3
test<- all7 %>% filter(return.pdol <=3 & return.pdol> -2)
qqPlot(test$return.pdol)
qqPlot(log(test$return.pdol+.97))
#have a look at the shape of return.pdol as bar graph
ggplot(test, aes(x=return.pdol)) + geom_histogram(aes(y=..density..), binwidth=.1)
ggplot(test, aes(x=log(test$return.pdol+.97))) + geom_histogram(aes(y=..density..), binwidth=.1)
```

@@

```{r}

### delete outliers! and variables that aren't by milestone
all7a<- all7 %>% filter(return.pdol <=3 & return.pdol> -2)
all7a<- all7 %>% select(-Paperless,-Innovation, -JobInvCount,-job.first.inv.email.Sent, 
                        -Total.Costs..AUD., -Stage, -Folders, -Total.Fee, -Disburse, -Subcon.fee,
                        -Job.Size, -Tot.Invoiced, -charge, -cost, -Dis.subcon, -hours,-profit,-balance,
                        -Role)

@@

```{r, echo=FALSE}
BT.lin<- function(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') {
        formula = paste("return.pdol ~ inv.mlsto + Discipline + client.count + Business +
                              Biz.size + Biz.type + Year + Num.days +
                              no.users + pc.contracttech + client.neginv + client.numinv + client.totinv +
                              pc.director + pc.midtech + pc.midpro + pc.gradpro + pc.seniortech + pc.seniorpro +
                              pc.pro + mean.peeps + hours.perday + num.inv + mean.inv + num.neginv + client.meaninv +
                              code.director + ProjEng.Pos", add.var, sep="+")
        if (type== 'aov') {
            model= aov(as.formula(formula)              
                      ,data= data)
            return(summary(model)) 
        }
        else{
                model=lm(as.formula(formula)                     
                        ,data= data)
                df<- as.data.frame(summary(model)$coefficients)
                df$var<-rownames(summary(model)$coefficients)
                colnames(df)[names(df) %in% 'Pr(>|t|)']<-'Pval'
                return(df %>% arrange(-abs(Estimate)))

@@

}
```

```{r}

# BT.lin(type= 'lm', data= all7a[1:1313,], add.var = 'Job.Type.Primary') %>% slice(1:20)
BT.lin(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') %>% slice(1:20)
BT.lin(type= 'lm', data= all7a[1314:2283,], add.var = 'Job.Type.Primary') %>% slice(1:10)
BT.lin(type= 'aov', data= all7a, add.var = 'Job.Type.Primary')
BT.lin(type= 'aov', data= all7a[1314:2283,], add.var = 'Job.Type.Primary')

@@

Most influential variables are:

* Business type
* director code
* Discipline
* Biz.type

Excluded variables include:

* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Primary
* Job.Detail.Secondary
* Job.Type.Primary
* Job.Type.Secondary
* State
* Type
* no.employees
* contact.count
* JD.Primary
* JD.Second
* dist
* timespan (won't know to begin with)
* Num.disc
* Inv.freq
* client.invfreq

# Correlation Analysis - Numeric variables with 'return.pdol' variable

First run Corrgram  - corrgram function
Run as type 'spearman' - non linear

```{r, echo=FALSE}

#### CORRELATION ANALYSIS

# str(all7a)
num.all<- all7a %>% select(client.count, no.employees, dist, charge.ph, no.users, pc.contracttech,
                           pc.director, pc.gradpro, pc.midpro, pc.midtech, pc.seniorpro, pc.seniortech, 
                           pc.unknown, pc.pro, pc.tech, Year, balance.mlsto,
                           timespan, Num.disc, Num.days, mean.peeps, hours.perday, hrs.mlsto, cost.mlsto, 
                           dis.sc.mlsto, 
                           inv.mlsto, return.pdol,
                           num.inv, mean.inv, Inv.freq, num.neginv, client.meaninv, client.invfreq, client.neginv, 
                           client.numinv,
                           client.totinv)
corrgram(num.all %>% select(client.count, charge.ph, no.users, pc.director, pc.gradpro, pc.midpro, 
                            pc.midtech, pc.contracttech, return.pdol,
                            pc.seniorpro, pc.seniortech, balance.mlsto,
                            pc.unknown, pc.pro, pc.tech, Year, Num.days, mean.peeps, hours.perday, hrs.mlsto, 
                            cost.mlsto,
                            dis.sc.mlsto, inv.mlsto, num.inv, mean.inv, client.meaninv, client.totinv,
                            timespan) %>% filter(complete.cases(.)), order=T, 
         lower.panel = panel.shade,
         upper.panel = panel.pie,
         text.panel = panel.txt,
         cor.method = 'spearman')
# summary(num.all)
# num.all[rowSums(is.na(num.all))>0,]
```

Now output cor.test results for all numeric variables using both pearson (linear) and kendall (non-linear) to compare.
Kendall does not have problems with ties

```{r, echo=FALSE}

#correlation by each variable against return.perdol individually - numeric variables only

cor.all<- c("client.count", "no.users", "pc.director", "pc.gradpro", "pc.midpro", 
            "pc.midtech", "pc.contracttech", "return.pdol","Inv.freq", 'num.neginv','client.invfreq','client.neginv',
            "pc.seniorpro", "pc.seniortech", "no.employees", "dist", "Num.disc",'client.numinv',
            "pc.unknown", "pc.pro", "pc.tech", "Year", "Num.days", "mean.peeps", "hours.perday", "hrs.mlsto", 
            "cost.mlsto",
            "dis.sc.mlsto", "inv.mlsto", "num.inv", "mean.inv", "client.meaninv", "client.totinv",
            "timespan")

summ<- data.frame("test"=NULL,
                  'var' = NULL,
                  'corr' = NULL,
                  'p.val' = NULL)

for(i in 1:length(cor.all)) {

        a = cor.test(all7a$return.pdol, all7a[,cor.all[i]], method = c('pearson'))

        b = cor.test(all7a$return.pdol, all7a[,cor.all[i]], method = c('kendall'))

        inter.summ = data.frame('test'= c('pearson','kendall'),
                                'var' = c(cor.all[i], cor.all[i]),
                                'corr' = c(a$estimate, b$estimate),
                                'p.val' = c(a$p.val, b$p.val))

        summ = rbind(summ,inter.summ)
}

summ$p.val <- format(summ$p.val, scientific=TRUE, digits = 3)
summ$p.val <- as.numeric(summ$p.val)
summ$corr <- round(summ$corr, 3)

Output ordered by p value
```{r, echo=TRUE}

summ %>% arrange(test, p.val)

Output ordered by correlation value - only 'significant' results to 5%

```{r}

summ %>% filter(p.val<= 0.05) %>% arrange(test, -abs(corr))

From this list it can be concluded what the most influential variables are. 
For the purposes of return.pdol prediction, cost.mlsto, hrs.mlsto, Num.days, dis.sc.mlsto,
num.neginv, Year (won't help in the future) cannot be known.

This leaves the following important variables:

```{r, echo=FALSE}
kable(
        summ %>% filter(p.val<= 0.05, test== 'kendall') %>% arrange(test, -abs(corr)) %>% 
                select(var, p.val, corr) %>%
                filter(var!= 'cost.mlsto', var!= 'hrs.mlsto', var!= 'Num.days', var!= 'dis.sc.mlsto',
                       var!= 'num.neginv',var!= 'Year', var!= 'return.pdol')
         )

# Strength of association with Categorical variables
